---
title: "Hello world MVP prototype"
output: rmarkdown::html_vignette
status: final
target-version: "0.3.0"
---
<!-- @required: status one of draft|final|deprecated -->
<!-- @required: target-version specified -->

The prototype is in this case an RMarkdown document format but anything could work.

## Links

* [FEATURE](/design/features/feat-001-prints-hello-world.md) - the hello world
* [FEATURE](/design/features/feat-002-greets-user-by-name.md) - greet by name
<!-- @required: A link to the features implemented -->

* [TESTDATA](/src/test/resources/test-data-001-mvp.csv)
<!-- @optional: A path to test data this prototype generates -->
<!-- if the prototype writes test data this should be present and the target exists -->

## Methods

The greet function uses the mathematical model based on the work of Einstein et al.

$$
\frac{1}{x} = \sqrt(y)
$$

In the case of a complex mathematical model the prototype as a quarto or RMarkdown file becomes part
of the documentation and write up, maybe as supplementary material to a journal article - could include visualisations.

```{r setup}
here::i_am("design/prototypes/prototype-001-mvp.Rmd")
```

## Prototype:

Prototype description and execution instructions:

* any required setup, tear down considerations.
* edge cases expected failures

```{r}
# A prototype function:
greet = function(name) {
  if (is.na(name)) name = "friend"
  return(paste0(c(
    "Hello world",
    sprintf("How are you, %s?",name)
  ),collapse="\n"))
}
```

## User testing:

Testing the prototype, might involve a html widget user interface, or a set of test cases:

```{r}
greet("Fred")
greet("Jack")
# Prototype inputs and results can be run by the developer and .
```

Visualisations of the prototype methods may be part of the documentation.

## Test data:

Generating test data from the prototype and writing it into the production code test cases:

```{r}

names = c("Fred", "Jack", NA)
results = lapply(names, greet)
test_data = tibble::tibble(name = names, result = unlist(results))

readr::write_csv(test_data, here::here("src/test/resources/test-data-001-mvp.csv"))

```
